\bf Title here

### 2020-08-31 paper/paper.tex
more changes of the section title, add new section on animated plots

\hypertarget{examining-the-interpolation-progress}{%
\subsection{Examining the interpolation
progress}\label{examining-the-interpolation-progress}}

@@

\hypertarget{understanding-the-optimisers-coverage-of-the-search-space}{%
\subsubsection{Understanding the optimiser's coverage of the search
space}\label{understanding-the-optimisers-coverage-of-the-search-space}}

@@

\hypertarget{a-problem-of-not-monotonic}{%
\subsection{A problem of not
monotonic}\label{a-problem-of-not-monotonic}}

@@

\hypertarget{a-more-complex-example-choosing-the-initial-value-for-polishing-parameter}{%
\subsection{A more complex example: Choosing the initial value for
polishing
parameter}\label{a-more-complex-example-choosing-the-initial-value-for-polishing-parameter}}

>>>>

\hypertarget{examining-the-optimisation-progress}{%
\subsection{Examining the optimisation
progress}\label{examining-the-optimisation-progress}}

@@

\hypertarget{understanding-the-optimisers-coverage-of-the-search-space}{%
\subsection{Understanding the optimiser's coverage of the search
space}\label{understanding-the-optimisers-coverage-of-the-search-space}}

@@

\hypertarget{a-problem-of-not-monotinic}{%
\subsection{A problem of not
monotinic}\label{a-problem-of-not-monotinic}}

@@
